Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-29 colt-21/cvx-flats.tex
Modifying figure 1

\begin{table}
	\begin{center}
	\begin{tabular}{p{12ex}|l|l|} 
		& \emph{Target loss}  & \emph{Target statistic}\\ \hline
		\emph{Discrete} & \textbf{Q1:} Classification  & \textbf{Q2:} Hierarchical prediction\\ 
		{\em prediction} & & \jessie{Need different example}\\ \hline 
		\emph{Continuous } & \textbf{Q3:} Least-squares regression & \textbf{Q4:} Variance estimation\\ 
		\emph{estimation}& & \\
		\hline
	\end{tabular}
\caption{The four quadrants of problem types, with an example of interest for each.}
\label{tab:quadrants}
\end{center}
\end{table}

@@

\tikzset{vertex/.style = {ellipse,draw,minimum width=10em, fill = white}}
\tikzset{edge/.style = {->,> = triangle 45, thick}}
\tikzset{node/.style = {anchor=above, sloped}}

\path[fill=blue, fill opacity = 0.1] (0,-4) -- (0,4) -- (14,4) -- (14,-4) -- cycle;
\draw[dashed, opacity = 0.4] (0,-4) -- (0,4);
\node[draw=none] at (3,3.5) {{\Huge$\Lcvx$}};
\node[draw=none] at (-3,3.5) {{\Huge$\L$}};

% vertices
\node[vertex] (consistent) at  (-9,3) {Consistency};
\node[vertex] (calibrated) at  (-9,-3) {Calibration (Q 1,3)};
\node[vertex] (indir-elic) at  (-3,0) {Indirect elicitation};

\node[vertex] (d-flats) at  (3,0) {$d$-flats in level sets};
\node[vertex] (q1-bounds) at (9,3) {$\conscvx$ bounds for Q1,2- Cor.~\ref{ref}};
\node[vertex] (q4-bounds) at (9,-3) {$\conscvx$ bounds for Q3,4- Theorem~\ref{ref}};

@@

\draw[edge] (d-flats) to node[above, sloped]{{\footnotesize Cor.~\ref{cor:Pcodim-flat-elic-relint-prop}}} (q4-bounds);
\draw[edge] (d-flats) to node[above, sloped]{\footnotesize {Cor.~\ref{cor:Pcodim-flat-single-val-prop}}} (q1-bounds);
\end{tikzpicture}
}
\end{center}
\caption{Flow and implications of results \jessie{Change}\raf{Suggested tweaks: larger font, lower vertical distance, newlines as needed (see what I did in Bartlett et al.\ to make that happen)}}
\label{fig:results-flow}
\end{figure}

>>>>

\begin{table}
	\begin{center}
	\begin{tabular}{p{12ex}|l|l|} 
		& \emph{Target loss}  & \emph{Target statistic}\\ \hline
		\emph{Discrete} & \textbf{Q1:} Classification  & \textbf{Q2:} Risk-averse classification\\ 
		{\em prediction} & & (Appendix~\ref{app:omitted-examples})\\ \hline 
		\emph{Continuous } & \textbf{Q3:} Least-squares regression & \textbf{Q4:} Variance estimation\\ 
		\emph{estimation}& & \\
		\hline
	\end{tabular}
\caption{The four quadrants of problem types, with an example of interest for each.}
\label{tab:quadrants}
\end{center}
\end{table}

@@

\tikzset{vertex/.style = {ellipse,draw,minimum width=10em, fill = white, font=\Large}}
\tikzset{edge/.style = {->,> = triangle 45, thick}}
\tikzset{node/.style = {anchor=above, sloped}}
\tikzstyle{every node}=[font=\Large]

\path[fill=blue, fill opacity = 0.1] (0,-3) -- (0,3) -- (16,3) -- (16,-3) -- cycle;
\draw[dashed, opacity = 0.3] (0,-3) -- (0,3);
\node[draw=none] at (3,2.5) {{\Huge$\Lcvx$}};
\node[draw=none] at (-3,2.5) {{\Huge$\L$}};

% vertices
\node[vertex] (consistent) at  (-11,2) {Consistency};
\node[vertex] (calibrated) at  (-11,-2) {Calibration (Q 1,3)};
\node[vertex] (indir-elic) at  (-4,0) {Indirect elicitation};

\node[vertex] (d-flats) at  (4,0) {$d$-flats in level sets};
\node[vertex, text width=45mm] (q1-bounds) at (12,2) {$\conscvx$ bounds for Q1,2. (Cor.~\ref{cor:fsd-bound})};
\node[vertex, text width=45mm] (q4-bounds) at (12,-2) {$\conscvx$ bounds for Q3,4. (Theorem~\ref{thm:bayes-risk-lower-bound})};

@@

\draw[edge] (d-flats) to node[above, sloped]{Cor.~\ref{cor:Pcodim-flat-elic-relint-prop}} (q4-bounds);
\draw[edge] (d-flats) to node[above, sloped]{Cor.~\ref{cor:Pcodim-flat-single-val-prop}} (q1-bounds);
\end{tikzpicture}
}
\end{center}
\caption{Flow and implications of results \jessie{Change}\raf{Suggested tweaks: larger font, lower vertical distance, newlines as needed (see what I did in Bartlett et al.\ to make that happen)}}
\label{fig:results-flow}
\end{figure}
